### 2015-04-16 README.Rmd
Minor changes to readme

Thomas E. White^1,7^, Rhiannon L. Dalrymple^2,7^, Daniel W. A. Noble^1,2,7^, James C. O’Hanlon ^1,7^, Daniel B. Zurek^3,7^, Kate D. L. Umbers^4,5,6,7^

^1^ Department of Biological Sciences, Macquarie University, North Ryde, NSW, Australia, 2109 ^2^ Evolution & Ecology Research Centre, School of Biological, Earth and Environmental Sciences, University of New South Wales, Kensington, NSW, Australia, 2022 ^3^ Department of Biological Sciences, University of Pittsburgh, Pittsburgh, PA, USA, 15260 ^4^ School of Biological Sciences, University of Wollongong, Wollongong, NSW, Austrlaia 2252 ^5^ Centre for Evolutionary Biology, University of Western Australia, Crawley, WA, Australia 6008 ^6^ School of Science and Health, University of Western Sydney Hawkesbury, NSW, Australia 2751

@@

# Source the knit_doc.R
source("R/knit_doc.R")

```

>>>>

Thomas E. White1, Rhiannon L. Dalrymple2, Daniel W. A. Noble1,2, James C. O’Hanlon 1, Daniel B. Zurek3, Kate D. L. Umbers4,5,6

1 Department of Biological Sciences, Macquarie University, North Ryde, NSW, Australia, 2109 2 Evolution & Ecology Research Centre, School of Biological, Earth and Environmental Sciences, University of New South Wales, Kensington, NSW, Australia, 2022 3 Department of Biological Sciences, University of Pittsburgh, Pittsburgh, PA, USA, 15260 4 School of Biological Sciences, University of Wollongong, Wollongong, NSW, Austrlaia 2252 5 Centre for Evolutionary Biology, University of Western Australia, Crawley, WA, Australia 6008 6 School of Science and Health, University of Western Sydney Hawkesbury, NSW, Australia 2751

@@

# Source the knit_doc.R
source("R/knit_doc.R")
```
